Cover Letter

### 2022-11-15 paper/paper/SPIE/article.tex
finalize

\documentclass[12pt]{spieman}  % 12pt font required by SPIE;
%\documentclass[a4paper,12pt]{spieman}  % use this instead for A4 paper
\usepackage{amsmath,amsfonts,amssymb}
\usepackage{graphicx}
\graphicspath{ {./figures/} }
\usepackage{setspace}
\usepackage{hyperref}
\usepackage{tocloft}
\usepackage{doi}
\usepackage{csquotes}
\MakeOuterQuote{"}
\usepackage{xr}
\externaldocument[S-]{supplementary}

@@

\affil[a]{St. Francis Xavier University, Department of Computer Science, 4130 University Avenue, Antigonish, Nova Scotia, Canada, B2G 2W5}
\affil[b]{St. Francis Xavier University, ACENET, 4130 University Avenue, Antigonish, Nova Scotia, Canada, B2G 2W5}

\affil[c]{St. Francis Xavier University, Department of Physics, 4130 University Avenue, Antigonish, Nova Scotia, Canada, B2G 2W5}

\affil[d]{Martinos Center for Biomedical Imaging, 149 Thirteenth Street, Suite 2301, Charlestown, Massachusetts, United States, 02129}
\affil[e]{Harvard Medical School, Department of Radiology, 25 Shattuck Street Boston, Massachusetts 02115, United States, 02129}
\affil[f]{Nova Scotia Health Authority, Research Affiliate, Nova Scotia, Canada}

>>>>

\documentclass[12pt]{spieman}  % 12pt font required by SPIE;
%\documentclass[a4paper,12pt]{spieman}  % use this instead for A4 paper
\usepackage{amsmath,amsfonts,amssymb}
\usepackage{graphicx}
\graphicspath{ {./figures/} }
\usepackage{setspace}
\usepackage{hyperref}
\usepackage{tocloft}
\usepackage{doi}
\usepackage{lineno}
\linenumbers
\usepackage{csquotes}
\MakeOuterQuote{"}
\usepackage{xr}
\externaldocument[S-]{supplementary}

@@

\affil[a]{St. Francis Xavier University, Department of Computer Science, 4130 University Avenue, Antigonish, Nova Scotia, Canada, B2G 2W5}
\affil[b]{St. Francis Xavier University, ACENET, 4130 University Avenue, Antigonish, Nova Scotia, Canada, B2G 2W5}
\affil[c]{St. Francis Xavier University, Department of Physics, 4130 University Avenue, Antigonish, Nova Scotia, Canada, B2G 2W5}
\affil[d]{Athinoula A. Martinos Center for Biomedical Imaging, 149 Thirteenth Street, Suite 2301, Charlestown, Massachusetts, United States, 02129}
\affil[e]{Harvard Medical School, Department of Radiology, 25 Shattuck Street Boston, Massachusetts, United States, 02115}
\affil[f]{Nova Scotia Health Authority, Research Affiliate, Nova Scotia, Canada}

### 2022-11-15 paper/paper/SPIE/cover_letter.tex
finalize

\documentclass[10pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage{csquotes}
\usepackage[british]{babel}
\usepackage{url}
\usepackage{graphicx}
\graphicspath{ {figures/} }
\usepackage{geometry}
\usepackage{amsmath}
\usepackage{graphicx}
% \usepackage[square,numbers]{natbib}
\usepackage[
    backend=biber,
    style=authoryear,
    natbib=true,
    sortlocale=en_US,
    url=false,
    doi=true,
    eprint=false
]{biblatex}
\addbibresource{report.bib}
\usepackage{fancyhdr}
\usepackage{color}
\definecolor{darkblue}{rgb}{0.,0.,0.4}
\definecolor{darkred}{rgb}{0.5,0.,0.}
\usepackage[pdftex,colorlinks=true,linkcolor=darkblue,citecolor=darkred,urlcolor=blue]{hyperref}

@@

We confirm that this work is original and has not been published elsewhere nor
is it currently under consideration for publication elsewhere.

@@

\begin{enumerate}
  \item employs RMT to generate reductions of the full voxelwise fMRI
        correlation matrix
  \item evaluates RMT-related metrics in a cross-validated predictive
        framework, instead of the more typical descriptive or explanatory
        frameworks
  \item systematically investigates the impact of the various methodological
        decisions involved in the findings
  \item makes all code used in the paper publicly available, including the release of a
        separate, general, open-source RMT
        library \citep{dm-bergerStfxecutablesEmpyricalRMTV12022} that will allow
        RMT metrics to be easily and reproducibly computed on a wide variety of
        data
\end{enumerate}

@@

\small
\noindent
\textbf{Corresponding Author}\\
Jacob Levman, PhD (jlevman@stfx.ca) \\
% Canada Research Chair in Bioinformatics \\
Department of Computer Science \\
St. Francis Xavier University \\

\noindent
\textbf{Additional Contacts} [should the corresponding author be unavailable]\\
Derek Berger (dberger@stfx.ca), Department of Computer Science, St. Francis Xavier University\\
Gurpreet S. Matharoo (gmatharo@stfx.ca), Department of Physics, St. Francis Xavier University

>>>>

\documentclass[10pt,letter]{article}
\usepackage[utf8]{inputenc}
\usepackage{csquotes}
\usepackage[british]{babel}
\usepackage{url}
\usepackage{graphicx}
\graphicspath{ {figures/} }
\usepackage{geometry}
\geometry{
  lmargin=2cm,
  rmargin=2cm,
  bmargin=2cm,
}
\usepackage{amsmath}
\usepackage{graphicx}
% \usepackage[square,numbers]{natbib}
\usepackage[
    backend=biber,
    style=authoryear,
    natbib=true,
    sortlocale=en_US,
    url=false,
    doi=true,
    eprint=false
]{biblatex}
\addbibresource{report.bib}
\usepackage{fancyhdr}
\usepackage{color}
\definecolor{darkblue}{rgb}{0.,0.,0.4}
\definecolor{darkred}{rgb}{0.5,0.,0.}
\usepackage[pdftex,colorlinks=true,linkcolor=darkblue,citecolor=darkred,urlcolor=blue]{hyperref}

@@

We confirm that this work is original and has not been published elsewhere nor
is it currently under consideration for publication elsewhere. However, a
poster of limited preliminary results related to this study was presented at
the International Symposium for Magnetic Resonance in Medicine 2021 annual
conference, and is available in abstract form \citep{bergerOpenSourceRandom2021}.

@@

\begin{enumerate}
  \item employs RMT to generate reductions of the full voxelwise fMRI
        correlation matrix
  \item evaluates RMT-related metrics in a cross-validated predictive
        framework, instead of the more typical descriptive or explanatory
        frameworks
  \item systematically investigates the impact of the various methodological
        decisions that affect the findings
  \item makes all code used in the paper publicly available, including the release of a
        separate, general, open-source RMT
        library \citep{dm-bergerStfxecutablesEmpyricalRMTV12022} that will allow
        RMT metrics to be easily and reproducibly computed on a wide variety of
        data
\end{enumerate}

@@

\small
\noindent
\textbf{Corresponding Author}\\
Jacob Levman, PhD (jlevman@stfx.ca) \\
\footnotesize
\hspace*{0.25cm}St. Francis Xavier University, Department of Computer Science  \\
\hspace*{0.25cm}Martinos Center for Biomedical Imaging, Massachusetts General Hospital \\
\hspace*{0.25cm}Harvard Medical School, Department of Radiology (jlevman@mgh.harvard.edu) \\
\hspace*{0.25cm}Nova Scotia Health Authority, Research Affiliate (jacob.levman@nshealth.ca) \\
\normalsize

\small
\noindent
\textbf{Additional Contacts} [should the corresponding author be unavailable]\\
Derek Berger (dberger@stfx.ca)\\
\footnotesize
\hspace*{0.25cm} St. Francis Xavier University, Department of Computer Science \\
\small
Gurpreet S. Matharoo (gmatharo@stfx.ca) \\
\footnotesize
\hspace*{0.25cm} St. Francis Xavier University, Department of Physics \\
\hspace*{0.25cm} St. Francis Xavier University, ACENET
\normalsize

% \affil[b]{St. Francis Xavier University, ACENET, 4130 University Avenue, Antigonish, Nova Scotia, Canada, B2G 2W5}

% \affil[c]{St. Francis Xavier University, Department of Physics, 4130 University Avenue, Antigonish, Nova Scotia, Canada, B2G 2W5}

% \affil[d]{Martinos Center for Biomedical Imaging, 149 Thirteenth Street, Suite 2301, Charlestown, Massachusetts, United States, 02129}
% \affil[e]{Harvard Medical School, Department of Radiology, 25 Shattuck Street Boston, Massachusetts 02115, United States, 02129}
% \affil[f]{Nova Scotia Health Authority, Research Affiliate, Nova Scotia, Canada}
